|

### 2022-03-27 04-Chp-Systematic-Review-Results.Rmd
Added number of studies by type and non-linearity P

The majority of included studies described non-randomised analyses, with the only two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on incidence of all-cause dementia in older adults. A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS). This leads to complications in the synthesis of these estimates due to the potential for double counting (see Section \@ref(sys-rev-res-AD)).

@@

<!----------------------------------------------------------------------------->
(ref:lipidsDoseResponse-cap) __Dose-response meta-analysis of total cholesterol on Alzheimer's disease__ - Non-randomised studies examining the association of lipids levels with Alzheimer's disease across several categories or "doses" of exposure were synthesised using a dose response meta-analysis. The reference dose was defined _a priori_ as 200 _mg/dL_, the cut-off of the "Normal"/"Optimal" category for total cholesterol as detailed in Table \@ref(tab:lipidLevels-table).

>>>>

The majority of included studies described non-randomised [(N = 74) and Mendelian randomisation (N=8)]{.correction} analyses, with the only two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on incidence of all-cause dementia in older adults. A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS). This leads to complications in the synthesis of these estimates due to the potential for double counting (see Section \@ref(sys-rev-res-AD)).

@@

<!----------------------------------------------------------------------------->
(ref:lipidsDoseResponse-cap) __Dose-response meta-analysis of total cholesterol on Alzheimer's disease__ - Non-randomised studies examining the association of lipids levels with Alzheimer's disease across several categories or "doses" of exposure were synthesised using a dose response meta-analysis. The reference dose was defined _a priori_ as 200 _mg/dL_, the cut-off of the "Normal"/"Optimal" category for total cholesterol as detailed in Table \@ref(tab:lipidLevels-table). [There was little evidence for a non-linear relationship (Wald-type test for deviation from linearity p = 0.46).]{.correction}
